---
title: "SLAPNAP Report"
author: "SLAPNAP Team"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r}
# get NAbs names from ENV variable
antibody_string <- Sys.getenv("Nab")
antibodies <- strsplit(antibody_string, split = ";")[[1]]
n_ab <- length(antibodies)
# load data
analysis_data_name <- list.files("/home/dat/analysis")
dat <- read.csv(paste0("/home/dat/analysis/", analysis_data_name), header = TRUE)
```

# Descriptives of endpoints

The NAbs studied in this analysis are `r antibodies`. Histograms of IC-50 and IC-80 for each individual NAb are shown in Figure \@ref(fig:histic50) and Figure \@ref(fig:histic80), respectively. Histograms for the predicted IC-50 an IC-80 based on the additive model are shown in Figure \@ref(fig:histcombn), while a histrogram of the predicted IIP is shown in Figure \@ref(fig:histiip).

```{r histic50, fig.cap = "Histogram of IC50 values for individual NAbs"}
if(n_ab > 1){
	tot_figs <- ifelse(n_ab%%2 == 0, n_ab, n_ab +1)
	layout(matrix(1:tot_figs, ncol = 2))
}
for(i in seq_len(n_ab)){
	this_name <- gsub("-", ".", paste0(antibodies[i], ".ic50.imputed"))
	hist(dat[ , this_name], main = antibodies[i],
	     xlab = "IC-50")
}
```

```{r histic80, fig.cap = "Histogram of IC80 values for individual NAbs"}
if(n_ab > 1){
	layout(matrix(1:tot_figs, ncol = 2))	
}
for(i in seq_len(n_ab)){
	this_name <- gsub("-", ".", paste0(antibodies[i], ".ic80.imputed"))
	hist(dat[ , this_name], main = antibodies[i],
	     xlab = "IC-80")
}
```

```{r histcombn, fig.cap = "Histogram of estimated IC50 and IC80 for combined NAbs. Top row = original scale; bottom row = log10 scale"}
layout(matrix(1:4, nrow = 2, byrow = TRUE))
hist(dat$pc.ic50, main = "", xlab = "Estimated IC-50")
hist(dat$pc.ic80, main = "", xlab = "Estimated IC-80")
hist(dat$log10.pc.ic50, main = "", xlab = expression(log[10]*" estimated IC-50"))
hist(dat$log10.pc.ic80, main = "", xlab = expression(log[10]*" estimated IC-50"))
```

```{r histiip, fig.cap = "Estimated IIP for combined NAbs"}
hist(dat$iip, main = "", xlab = "Estimated IIP")
```

```{r checkmiss}
n_row_prev <- nrow(dat)
dat <- dat[complete.cases(dat),]
n_row_now <- nrow(dat)
```
There were `r n_row_prev` observations extracted from the CATNAP database. There were `r n_row_now` observations with complete sequence data that were used in the analysis.

# Super Learner

```{r load_super_learners}
fit_ic50 <- get(load("/home/slfits/cvfit_pc.ic50.RData"))
# fit_ic80 <- get(load("/home/slfits/cvfit_pc.ic80.RData"))
# fit_iip <- get(load("/home/slfits/cvfit_iip.RData"))
```

Figure \@ref(fig:plotic50) shows the cross-validated performance for predicting IC-50. 

```{r plotic50, fig.cap = "Cross-validated performance of Super Learner for estimated IC-50"}
# TO DO: Bring in code to plot CV-R2 from flu projects
plot(fit_ic50)
```